### 2014-11-18 docs/ms.Rmd
Integrated Rhi's changes into ms.Rmd

Keywords: #colsci, visual ecology, spectrophotometry, tetrahedral color space, quantum catch, pigment, structural color, thermoregulation, signaling, PAVO, colormetrics, visual modeling, melanism, sexual selection.

## Abstract

## Introduction
Since Thayer [-@thayer_concealing_1909], Poulton [-@poulton_colours_1890] and Wallace [-@wallace_natural_1891] generations of biologists have endeavored to explain the mechanisms and functions of animal and plant coloration. For these biologists, identifying best practice in measuring color and color pattern and in determining how other species see colour has been a great challenge. Over the past 150 years biologists, both independently and in collaboration with physicists and chemists, have developed a range of techniques used to measure and analyse animal and plant coloration including spectrophotometry (also called spectroradiometry, spectroscopy ETC), photography and visual modeling.

The application of spectrophotometry to questions in ecology and evolution revolutionized the field [@dyck_determination_1966]. Before the widespread use of spectrophotometry, researchers assigned categorical color descriptions, arbitrary rankings or scores [e.g. @aldrich_ecogeographic_1991; @wheelwright_colors_1985] or matched paint swatches or munsell chip ratings based on their own visual assessment [e.g. @burtt_analysis_1986; @key_temperature_1954]. Although no doubt applied carefully, these techniques limited progress in the field. For example, many researchers designed color assessment methods specifically for their projects [e.g. @aldrich_ecogeographic_1991] rendering data by different researchers incomparable. This was/is especially problematic when different measurement techniques are used on the same species (e,g, refXXX vs ref XXX). Also, human vision, insensitive to ultraviolet wavelengths, is inherently different to most other animals such as avian and reptilian tetrachromats, and insect trichromats [@bennett_sexual_1994](MORE). Human perception of color, and variation therein, is not only biologically irrelevant to most systems, but it can lead to erroneous conclusions [@bennett_sexual_1994; @endler_measurement_1990].

Measuring reflectance spectra is now a reasonably inexpensive and convenient technique. Spectrophotometry allows the capture of quantitative and arguably repeatable data and has been rapidly taken up by researchers the field. However one drawback to spectrophotometry, is the ease with which erroneous data can be captured if attention is not paid to finer details of spectrum capture. For example, the angle from which spectra are taken [@santos_strong_2007], consistent calibration of light and dark standards, the distance between light source and object, the expectations of the researcher and the size, shape, glossiness or iridescence of the specimen [@andersson_quantifying_2006; @kemp_ornamental_2008; @meadows_quantifying_2011; @schaefer_birds_2008], can all contribute to potentially skewed data or alter results. Experience, guidance and objectivity are necessary to ensure data are consistent and representative of the subject and to ensure repeatability, conditions under which data were collected must be reported exactly.

In conjunction with spectrophotometry, digital photography is increasingly being implemented in color quantification. High-resolution cameras are now inexpensive and portable, allow instantaneous sampling of multiple colour patches, and can produce highly repeatable images [@mckay_use_2013]. The main challenges for gathering and using color data from photographs are ensure correct standardization methods such as linearization are consistent lighting [@stevens_using_2007]. Crucially, most digital cameras used in color science are consumer products designed for human visual color space and hardware modifications for ultraviolet and infrared imaging are necessary [e.g. @chiao_visualization_2009; @mckay_use_2013], making photography complementary, rather than superior to spectrophotometry.

Expansion in the availability of objective methods for the measurement of color has been matched by advances in theory and analysis. In particular, the development of sensory models has produced significant insights into the way in which colorful stimuli are perceived [@chittka_colour_1992; @endler_comparing_2005; @vorobyev_receptor_1998]. Where the receptor sensitivities of an animal’s visual system are known, the physiological response of that animal’s visual system when viewing a given color can be predicted.

Sensory models typically attempt to describe the subjective perception of color or brightness information as a function of an object’s reflectance, the ambient illumination, and a receiver’s sensory system [e.g. @endler_comparing_2005; @vorobyev_receptor_1998]. Furthermore, an animal’s ability to distinguish between reflectance spectra can then be predicted based on the differential responses of a visual system to varying reflectance spectra. This approach enables researchers to move beyond purely quantitative comparisons of reflectance spectra and adopt biologically relevant perspectives of signal receivers to test/formulate hypotheses.  
Although relatively easy to implement and potentially powerful, sensory models are built on multiple assumptions about the way in which stimuli are visually and cognitively processed that can dramatically shape the results of a given analysis [@lind_avian_2009; @pike_preserving_2012]. For example, Vorobyev et al.’s [-@vorobyev_receptor_1998; @vorobyev_colour_2001] widely used receptor-noise model requires researchers to specify the form of receptor quantum catches (i.e. raw versus log-transformed), the use of any color constancy mechanism (e.g. von Kries), as well as the photoreceptor signal-to-noise ratios, their relative densities, and the type of noise predominating (i.e. neural and/or receptor noise). These data are only available for a small number of model species, such as honeybees, and so assumptions and extrapolations are necessary when models are applied to related species. Unless the biological rationale underlying every parameter choice is clearly understood, justified, and reported, such analyses may become ineffective, especially when comparing results between studies [@pike_preserving_2012].

Since the repeatability and transparency of science is paramount, it is imperative that we regularly and constructively reflect on our own practices [@alsheikh_public_2011; @sandve_ten_2013]. The potential for detrimental subjectivity in color measurement and the mathematical opacity of visual models for the average colour scienctist means that, as in any field, is it critical that methods are reported rigorously. Methods reporting should ideally have well defined standards such that sufficient detail is provided to allow comprehensive peer review, precise replication, cross-study comparison and data sharing [@alsheikh_public_2011](Ask Rob Lanfear). The aims of this paper are to (a) review methods reporting in papers published on colour in 2013 from 20 top tier journals and (b) provide a set of recommendations for best-practice in reporting on the most common methods. Our hope is that this instructional provides a useful set of guidelines to improve the reproducibility and transparency of studies on color.

@@

We developed a list of metrics we deemed critical to be reported for reproducibility of color methods and analysis loosely based on Andersson and Prager [-@andersson_quantifying_2006] and Montgomerie [@montgomerie_analyzing_2006] (Table 1 and 2). These included quantitative methods including spectrophotometric and photographic techniques, but not qualitative methods such as the use of Munsell chips or paint swatches. For visual modeling techniques we characterized a set of criteria required for reproducing the analysis (Table 2).

@@

To determine the current state of methods reporting in the field we searched for papers from 2013 in 23 top color science journals (_Animal Behaviour_, _Behavioral Ecology_, _Journal of Experimental Biology_, _Biology Letters_, _Proceedings of the Royal Society B: Biological Sciences_, _Biological Journal of the Linnean Society_, _Ethology_, _The American Naturalist_, _Ecology Letters_, _Journal of Evolutionary Biology_, _American Journal of Botany_, _Evology and Evolution_, _Oikos_, _Ecology_, _Journal of Ecology_, _Behavioral Ecology and Sociobiology_, _Current Zoology_, _Naturwissenschaften_, _New Phytologist_, _PLoS ONE_, _Evolution_, _Functional Ecology_, _Ethology_). For each of the journals, we used the Boolean search terms 'colour*', 'color*' or 'spectra*' and searched for these in the title or abstract from each of the journal home pages. We read the titles and abstracts of each paper and included only those papers that explicitly used either a spectrophotometer or camera to quantify colour signals. We excluded papers that were: 1) review papers; 2) methodological papers; 3) papers quantifying colour pattern; and 4) papers taking microspectrophotometric measurments of retinal absorbance. To review the large number of papers returned from the searches, journals were haphazardly divided up between the authors. In order to reduce the risk of observer bias in our scoring, papers were read and reassessed by a total of three authors. Any discrepancies between the assessor scores were discussed and agreed upon prior to analysis. We then tabulated what details of the methods were reported against our criteria.

Our search returned a total of 216 papers, however, only `r nrow(coldat)` met our criteria and were included in the final analysis. Overall, `r specs+both` studies used a spectrophotometer to measure color, while `r cam+both` used a camera. Of these studies, `r both` quantified color using both a spectrophotometer and a camera. Reporting of the make and model of the spectrophotometer and camera was high (Figure 1 - Specs = `r round(specModel, digits = 2)`% and Cameras = `r round(camModel, digits = 2)`%), however, only `r round(CamLight, digits = 2)`%  and `r round(specLight, digits = 2)`% of camera and spec studies reported a light source. In addition, the number of reflectance spectra and pixels averaged were only reported in `r round(specAVG, digits = 2)`% and `r round(camAVG, digits = 2)`% of the studies, respectively. Surprisingly, of the spec studies, dark standards were only reported in `r round(drk_std, digits = 2)`% of the studies, while white standards were reported in `r round(white_stdspec, digits = 2)`%. Studies quantifying spectral reflectance also often did not report the integration time of the spectrophotmeter (`r round(intTime, digits = 2)`%) or the angle (`r round(angle, digits = 2)`%) or the distance (`r round(dist, digits = 2)`%) the probe was from the color patch.

Analysis varied across studies but, overall `r analysisType[1]` analyzed their data by generating colormetric (brightness, hue, chroma) variables whereas `r analysisType[4]` used visual models, `r analysisType[2]` used multiple analysis types (e.g. visual model and colourmetric) and `r analysisType[3]` did other forms of analysis (e.g. RGB, PCA's, GLMMs etc.). Of the studies quantifying colour using spectral reflectance curves `r analysisTypeSpec[1]` used colormetric measures, `r analysisTypeSpec[2]` used multiple analyses, `r analysisTypeSpec[4]` used visual models and `r analysisTypeSpec[3]` used other forms of analysis. Studies using colormetric measurements defined their measure of brightness, hue and/or chroma in `r round(col_def, digits = 2)`% of the studies.

Most studies using visual models analysed their data using receptor noise models (`r vismod_type[3]` of `r sum(vismod_type)` studies) while others used hexagon (`r vismod_type[1]` studies) or tcs (`r vismod_type[4]` studies). Case specific models were used in `r vismod_type[2]` cases. Overall, `r round(prop_irrad, digits =2)`% reported the type of irradiance, `r round(prop_spvismod, digits = 2)`% the species used in their visual model and `r round(propvis_mod_param, digits = 2)`% made explicit mention of the parameters they used (i.e. cone densities, neural vs quantum catchs etc.) in their methods. The background used in visual models was reported `r round(prop_bkg, digits = 2)`% of the time. The type of visual noise authors assumed was reported in `r round(prop_noise, digits = 2)`% of the studies. In addition, explicit mention of the type of quantum catche (`r round(prop_qcatch, digits = 2)`% of studies) or whether photoreceptor adaptation (`r round(prop_adap, digits = 2)`%) was accounted for in visual models was not common.

While some of the values reported above seem alarming, it is important to note that papers often made reference to previous work for various methods (`r round(ref_stud, digits = 2)`%) and so these figures are slightly liberal given that referenced work may have comprehensively covered some of these criteria. Despite this, many of the studies that did not reference previous work were lacking in their reporting of many aspects of our criteria suggesting the need for more comprehensive reporting of data collection and analysis methods within studies.

@@

Our review of recent colour literarure highlights some major reporting gaps that will hinder the reproducibility of studies quantifying colour signals. While we recognize that journals have space limitations and that work may reference previous methological and analytical details, we strongly beleive that studies can do a much better job reporting details which are essential to the transparency and reproducibility of their work. When possible, we also recommend that authors justify data capture and analytical approaches - something few studies we investiagted expliclty stated. While all criteria are important some deserve special attanetion. In particular we found that colour scientists could do a much better job reporting light sources, number of pixel and spectra averaged used for analysis and the type of standards used. More improtantly, the distance and angle should be standard reporting for all studies using spectrophotomtry. These all have important consequences on downstream analysis and the reproducibility of colour signal quantification. As we all know, a picture can say 1000 words and we recommend the incoperation of spectral reflectance curves were possible as it provides insight on the colour signal, which is visually appealing and easy to understand by most readers. Surprisingly, we found that only `r round(fig, digits = 2)`% of studies using spectral reflectance data had an explicit figure in their paper showing these curves. Visual models were regularly used to analyse spectral data, something we welcome. However, there were many important aspects of the analysis that were seldom reported, inclding the type of quantum catch used, whether photoreceptor adaptation was accounted for and the type of neural noise used in receptor noise models. Photoreceptor densities should also be reported where possible even if using standard avian photorecptor densities.

In conclusion, our objective in this paper was not to point to single studies and lay blame, but to highlight an important gap in reporting that can influence the reproducibility of colour research and cross taxa comparisons. Indeed, even in our own work [@umbers_bright_2013] we have failed to report important details, which in resptrospec can lead to confusion about how such data were collected and analysed. Nontheless, our critisim of reporting is meant to be constructive and is not to say that studies lacking improtant details are not excellent works, but it is only through critical appraisal and colleageal discussion that we can identify these gaps and constructively contribute to the growth of our field. Such assessments are particlularly important in an age where accountability, transparency and reproducibility of are utmost importance. We hope our critical evaluation of recent litearture has highlighted a need for more careful reporting of how colour signals have been measured and analysed. We beleive that part of the issue is simply that researchers seldom have clear guidelines to follow when undertaking research and miss what might be important aspects of their methods and analysis that need to be reported. We therefore hope that our paper will help estbalish more uniform reporting guidelines in the literature so that we can continue an exciting era of colour signal research in the life sciences.

>>>>

Keywords: #colsci, spectrometry, photography, visual ecology, pigment, structural colour, visual modeling, methodology

## Abstract
The colours of plants and animals have long fascinated biological scientists, but it is only recently that quantitative colour measurement techniques have become readily available. Spectrometry and digital photography are now relatively accessible and common techniques for the appraisal of biological colour, however, their rapid uptake has not been followed up by clear guidelines on which methodological details are crucial to report. We identified a number of details regarding measurement and analysis of colouration which have the potential to affect the outcomes of research. We reviewed reporting of relevant methodology in the 2013 literature on biological colour, and have outlined explicit recommendations for future research. In providing a constructive criticism of current practices, and identifying areas for improvement, we aim to better the accountability, transparency and reproducibility of colour research in the life sciences.

## Introduction
Since Thayer [-@thayer_concealing_1909], Poulton [-@poulton_colours_1890] and Wallace [-@wallace_natural_1891] generations of biologists have endeavored to explain the mechanisms and functions of animal and plant colouration. For scientists of this discipline, identifying best practice in measuring colour and colour pattern and in determining how other species see colour has been a great challenge. Over the past 150 years biologists, both independently and in collaboration with physicists and chemists, have developed a range of techniques used to measure and analyse biological colouration including spectrometry (also called spectroradiometry, spectrophotometry etc.), photography, and visual modeling.

The application of spectrometry to questions in ecology and evolution revolutionized the field [@dyck_determination_1966]. Before the widespread use of spectrometry, researchers assigned categorical colour descriptions, arbitrary rankings or scores [e.g. @aldrich_ecogeographic_1991; @bailey_latitudinal_1978; @wheelwright_colors_1985] or matched paint swatches or munsell chip ratings based on their own visual assessment [e.g. @burtt_analysis_1986; @key_temperature_1954]. Although no doubt applied carefully, these techniques limited progress in the field. For example, many researchers designed colour assessment methods specifically for their projects [e.g. @aldrich_ecogeographic_1991; @bailey_latitudinal_1978] rendering data by different researchers incomparable. This is especially problematic when different measurement techniques are used on the same species [e.g. the house finch _Carpodacus mexicanus_; @aldrich_origin_1978; @hill_female_1990]. Also, human vision, insensitive to ultraviolet wavelengths, is inherently different to most other animals such as avian and reptilian tetrachromats, and insect trichromats [@bennett_sexual_1994; @douglas_spectral_2014]. Human perception of colour is not only biologically irrelevant to most systems, but can lead to erroneous conclusions [@bennett_sexual_1994; @endler_measurement_1990].

Measuring reflectance spectra is now a reasonably inexpensive and convenient technique. Spectrometry allows the capture of quantitative and arguably repeatable data and has been rapidly taken up by researchers the field. However one drawback to this methodology, is the ease with which erroneous data can be collected if attention is not paid to finer details of spectrum capture. The angle from which spectra are taken [@santos_strong_2007], consistent calibration of light and dark standards, the distance between light source and object, the expectations of the researcher and the size, shape, glossiness or iridescence of the specimen [@andersson_quantifying_2006; @kemp_ornamental_2008; @meadows_quantifying_2011; @schaefer_birds_2008], can all contribute to potentially skewed data or alter results. Experience, guidance and objectivity are necessary to ensure data are consistent and representative of the subject. To ensure repeatability, the conditions under which data were collected must be reported exactly.

In conjunction with spectrometry, digital photography is increasingly being implemented in colour quantification. High-resolution cameras are now inexpensive and portable, allow instantaneous sampling of multiple colour patches, and can produce highly repeatable images [@mckay_use_2013]. The main challenge for gathering and using colour data from photographs is ensuring correct standardization methods, such as linearization, and consistent lighting [@stevens_using_2007]. Crucially, most digital cameras used in colour science are consumer products designed for human visual colour space, and hardware modifications for ultraviolet and infrared imaging are generally necessary [e.g. @stevens_colour_2013], making photography complementary, rather than superior to spectrometry.

Expansion in the availability of objective methods for the measurement of colour has been matched by advances in theory and analysis. In particular, the development of sensory models has produced significant insights into the way in which colourful stimuli are perceived [@chittka_colour_1992; @endler_comparing_2005; @vorobyev_receptor_1998]. Where the receptor sensitivities of an animal’s visual system are known, the physiological response of that animal’s visual system when viewing a given colour can be predicted.

Sensory models typically attempt to describe the subjective perception of colour or brightness information as a function of an object’s reflectance, the ambient illumination, and a receiver’s sensory system [e.g. @endler_comparing_2005; @vorobyev_receptor_1998]. These models enable researchers to move beyond purely quantitative comparisons of reflectance spectra and adopt biologically relevant perspectives of signal receivers to test/formulate hypotheses. Although relatively easy to implement and potentially powerful, sensory models are built on multiple assumptions about the way in which stimuli are visually and cognitively processed that can dramatically shape the results of a given analysis [@lind_avian_2009; @pike_preserving_2012]. For example, Vorobyev et al.’s [-@vorobyev_receptor_1998; @vorobyev_colour_2001] widely used receptor-noise model requires researchers to specify the form of receptor quantum catches (i.e. raw versus log-transformed), the use of any colour constancy mechanism (e.g. von Kries), as well as the photoreceptor signal-to-noise ratios, their relative densities, and the type of noise predominating (i.e. neural and/or receptor noise). These data are only available for a small number of model species, such as honeybees, and so assumptions and extrapolations are necessary when models are applied to related species. Unless the biological rationale underlying every parameter choice is clearly understood, justified, and reported, such analyses may become ineffective, especially when comparing results between studies [@pike_preserving_2012].

Since the repeatability and transparency of science is paramount, it is imperative that we regularly and constructively reflect on our own practices [@alsheikh_public_2011; @sandve_ten_2013]. The potential for subjectivity in colour measurement and the mathematical opacity of visual models for the average colour scientist means that, as in any field, is it critical that methods are reported rigorously. Methods reporting should ideally have well defined standards such that sufficient detail is provided to allow comprehensive peer review, precise replication, cross-study comparison and data sharing [@alsheikh_public_2011]. The aims of this paper were to (a) review methods reporting in papers published on colour in 2013 from 22 top tier journals and (b) provide a set of recommendations for best-practice in reporting on the most common methods. Our hope is that this paper will provide a useful set of guidelines to improve the reproducibility and transparency of studies on colour.

@@

We developed a list of metrics we deemed critical to be reported for reproducibility of colour methods (Table 1) and analysis (Table 2), loosely based on Andersson and Prager [-@andersson_quantifying_2006] and Montgomerie [@montgomerie_analyzing_2006]. These included quantitative methods including spectrophotometric and photographic techniques [as in @kemp_ornamental_2008; @chiao_visualization_2009] but not qualitative methods such as the use of Munsell chips or paint swatches [as in @hogstad_gloger_2009]. For visual modeling techniques we characterized a set of criteria required for reproducing the analysis (Table 2).

@@

To determine the current state of methods reporting in the field we searched for papers from 2013 in 22 top colour science journals (_Animal Behaviour_, _Behavioral Ecology_, _Journal of Experimental Biology_, _Biology Letters_, _Proceedings of the Royal Society B: Biological Sciences_, _Biological Journal of the Linnean Society_, _Ethology_, _The American Naturalist_, _Ecology Letters_, _Journal of Evolutionary Biology_, _American Journal of Botany_, _Ecology and Evolution_, _Oikos_, _Ecology_, _Journal of Ecology_, _Behavioral Ecology and Sociobiology_, _Current Zoology_, _Naturwissenschaften_, _New Phytologist_, _PLoS ONE_, _Evolution_, _Functional Ecology_). For each of the journals, we used the Boolean search terms 'colour*', 'color*' or 'spectra*' and searched for these in the title or abstract from each of the journal home pages. We read the titles and abstracts of each paper and included only those papers that explicitly used either a spectrophotometer or camera to quantify colour signals. We excluded papers that were: 1) review papers; 2) methodological papers; 3) papers quantifying colour pattern; and 4) papers taking microspectrophotometric measurments of retinal absorbance. To review the large number of papers returned from the searches, journals were haphazardly divided up between the authors. In order to reduce the risk of observer bias in our scoring, papers were read and reassessed by a total of three authors. Any discrepancies between the assessor scores were discussed and agreed upon prior to analysis. We then tabulated what details of the methods were reported against our criteria. The data along with analysis script can be found at: https://github.com/daniel1noble/colsci_rep (TODO: GIVE IT A DOI?). We have kept the papers used in our dataset annoymous to avoid accusing specific colleagues of inadvertant reporting. We feel that the issue of reporting is something attributable to the ambiguity and lack of guidelines in our field and not something specific to individual research groups.

Our search returned a total of 216 papers, however, only `r nrow(coldat)` met our criteria and were included in the final analysis. Overall, `r specs+both` studies used a spectrometer (henceforth "spec") to measure colour, while `r cam+both` used a camera. Of these studies, `r both` quantified colour using both a spec and a camera. Reporting of the make and model of the spec and camera was high (Figure 1, spectrometers = `r round(specModel, digits = 2)`% and cameras = `r round(camModel, digits = 2)`%), however, only `r round(CamLight, digits = 2)`%  and `r round(specLight, digits = 2)`% of camera and spec studies reported a light source. In addition, the number of reflectance spectra and pixels averaged were only reported in `r round(specAVG, digits = 2)`% and `r round(camAVG, digits = 2)`% of studies, respectively. Surprisingly, dark standards were only reported in `r round(drk_std, digits = 2)`% of the spec studies, while white standards were reported in `r round(white_stdspec, digits = 2)`%. Studies quantifying spectral reflectance often did not report the integration time of the spectrophotmeter (`r round(intTime, digits = 2)`%), or the angle (`r round(angle, digits = 2)`%) or distance (`r round(dist, digits = 2)`%) the probe was from the colour patch.

Analysis varied across studies. Overall `r analysisType[1]` papers analyzed  data by generating colourimetric variables [i.e. 'spectral' measures of hue, saturation, and/or brightness; @montgomerie_analyzing_2006] whereas `r analysisType[4]` used visual models, `r analysisType[2]` used multiple analysis types, and `r analysisType[3]` used other forms of analysis (e.g. purely statistical analyses, such as PCA's on reflectance spectra). Of the studies quantifying colour using spectral reflectance curves `r analysisTypeSpec[1]` used colourimetric measures, `r analysisTypeSpec[2]` used multiple analyses, `r analysisTypeSpec[4]` used visual models and `r analysisTypeSpec[3]` used other forms of analysis. Studies using colourimetric measurements defined their measure of brightness, hue and/or chroma in `r round(col_def, digits = 2)`% of the studies.

Most studies using visual models analysed their data using receptor-noise models (`r vismod_type[3]` of `r sum(vismod_type)` studies), while others used a hexagonal (`r vismod_type[1]` studies), or tetrahedral colour space (`r vismod_type[4]` studies) approach. Case specific models were used in `r vismod_type[2]` papers. Of visual modelling papers, `r round(prop_irrad, digits =2)`% reported the type of irradiance when necessary, `r round(prop_spvismod, digits = 2)`% the species modelled as a receiver, and `r round(propvis_mod_param, digits = 2)`% made explicit and complete mention of the parameters they used (e.g. cone densities, signal-to-noise ratios). The background used in visual models was reported `r round(prop_bkg, digits = 2)`% of the time. The type of receptor noise modelled was reported in only `r round(prop_noise, digits = 2)`% of the studies. Explicit mention of the type of quantum catch (`r round(prop_qcatch, digits = 2)`% of studies), or whether photoreceptor adaptation (`r round(prop_adap, digits = 2)`%) was modelled, was not common.

While some of the values reported above seem alarming, it is important to note that papers often made reference to previous work for various methods (`r round(ref_stud, digits = 2)`%), so these figures are slightly liberal given that referenced work may have comprehensively covered some of these criteria. Despite this, many of the studies that did not reference previous work were lacking in their reporting of many aspects of our criteria suggesting the need for more comprehensive reporting of data collection and analysis methods within such studies.

@@

Our review of recent colour literature highlights some important reporting gaps that will hinder the reproducibility of studies of biological colouration. While we recognize that journals have space limitations and that work may reference previous methological and analytical details, we strongly believe that researchers can do a better job of reporting details which are essential to the transparency and reproducibility of their work.  While all criteria are important, some deserve special attention. In particular, we found that colour scientists could do a better job reporting light sources, the numbers of pixels or spectra averaged, and the type of standards used. More importantly, the probe distance and angle should be standard reporting for all studies using spectrometry. Visual models were regularly used to analyse spectral data, something we welcome. However, there were many important aspects of the analysis that were seldom reported, including the type of quantum catch used, whether photoreceptor adaptation was modelled and the type of neural noise used in receptor-noise models. Photoreceptor densities should also be reported where possible even if using standard avian photorecptor densities. These all have important consequences on downstream analysis and the reproducibility of colour signal quantification [e.g. @kemp_ornamental_2008; @santos_comparison_2007]. It is said that a picture is worth 1000 words, and we recommend the presentation of spectral reflectance curves where possible; these figures are visually appealing and allow for the rapid assesment of the nature and quality of the data, independent of downstream processing. Surprisingly, we found that only `r round(fig, digits = 2)`% of studies using spectral reflectance data had a figure showing these curves. When possible, we also recommend that authors justify data capture and analytical approaches - something few studies we investigated explicitly outlined.

Our objective in this paper was not to point out single studies, but to highlight an important gap in reporting that can influence the reproducibility of colour research and cross-study comparisons. By no means do we wish to say that studies lacking important details are not of significant value. Indeed, even in our own work [e.g. @umbers_bright_2013] we have failed to report important details, which in retrospect can lead to confusion about how such data were collected and analysed. This review of reporting is aimed at providing constructive criticism; it is only through critical appraisal and collegial discussion that we can identify such gaps as areas for improvement, and constructively contribute to the growth of our field. Such assessments are particularly important in an age where accountability, transparency and reproducibility are of utmost importance.

We believe that part of the issue at hand is simply that many researchers seldom have clear guidelines to follow when undertaking research, and may overlook outlining important aspects of methodology and analysis.We hope our critical evaluation of recent literature has highlighted a need for more careful description of how colour signals have been measured and analyzed. We are optimistic that this may help establish uniform reporting guidelines for publication, and to continue the advance of an exciting era in colour research.
